ComBatLS Replication Results

### 2025-01-16 paper_replication_results.Rmd
finish removing FDR correction from sex-bias tests in replication

```{r}
noext.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext.sex.test.df <- bind_rows(noext.sex.test.list)
```

@@

```{r}
noext.sex.test.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  #geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = c("lightblue", "red"))
```

@@

next.t.test.cent.sex.test.med <- noext.sex.testmed %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 6,
                           dataset=="cf.lm" ~ 9,
                           dataset=="cf.gam" ~ 9.5,
                           dataset=="cf.gamlss" ~ 5))

t.test.cent.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig_fdr, fill=dataset), position="dodge")

next.t.test.cent.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig_fdr, fill=dataset), position="dodge")

sex_bias_density_plt_noext <- noext.sex.testmed %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos*100, y=y_pos),
              data = next.t.test.cent.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
ggsave(filename="figs/sex_bias_density_plt_noext.png", sex_bias_density_plt_noext, height=7, width=10, units="in")
```

@@

```{r}
z.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.sex.test.df <- bind_rows(z.sex.test.list)
```

@@

```{r}
z.sex.test.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  #geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = c("lightblue", "red"))
```

@@

```{r}
#look by feature type
z.sex_bias_hist_plt <- z.sex.test.df %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss" | dataset == "cf.lm") %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  mutate(pheno = gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    perm = as.factor(sub("perm-0", "", perm))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm), alpha=0.3, position="identity", bins=40) +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free", labeller = labeller(dataset = as_labeller(dataset_names))) +
  theme_linedraw(base_size=12) +
  theme(legend.position = "none") +
  labs(x="Male - Female Median Centile Errors", y="Number of Features") +
  ggtitle("Sex differences in median centile errors across 100 sampling replications")
ggsave(filename="figs/z.sex_bias_hist_plt.z.png", sex_bias_hist_plt)
```

@@

t.test.z.sex.test.med <- z.sex.test.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            t.test.stat = tidy(t.test(median_of_median_sex_diff))$statistic,
            t.test.df = tidy(t.test(median_of_median_sex_diff))$parameter,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(z.sex.test.med$dataset))*length(unique(z.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 155,
                           dataset=="cf.lm" ~ 360,
                           dataset=="cf.gam" ~ 345,
                           dataset=="cf.gamlss" ~ 125))

#pretty table
t.test.z.sex.test.med_tbl <- t.test.z.sex.test.med %>%
  dplyr::select(dataset, pheno_cat, t.test.est, t.test.stat, t.test.df, p.val_fdr, sig_fdr) %>%
  mutate(dataset = case_when(dataset == "cf" ~ "ComBat w/o Covariates",
                                   dataset == "cf.lm" ~ "Linear ComBat",
                                   dataset == "cf.gam" ~ "ComBat-GAM",
                                   dataset == "cf.gamlss" ~ "ComBatLS")) %>%
  rename("ComBat Method" = dataset,
         "Phenotype Category" = pheno_cat,
         "Estimate" = t.test.est,
         "t-statistic" = t.test.stat,
         "dfs" = t.test.df,
         "p-value (FDR-corrected)" = p.val_fdr,
         "Significance" = sig_fdr) %>%
  gt() %>%
  tab_style(style = list(cell_fill(color = "gray95")),
    locations = cells_row_groups()) %>%
  tab_options(column_labels.font.weight = "bold") %>%
  tab_header(title = "One-sided t-tests of sex differences in z-score errors across 100 replications")
gtsave(t.test.z.sex.test.med_tbl, filename="figs/z_median_sexdiff_table.png")
```

@@

t.test.z.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig_fdr, fill=dataset), position="dodge")

z.sex_bias_density_plt <- z.sex.test.med %>%
  dplyr::filter(dataset != "cf") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos, y=y_pos),
              data = t.test.z.sex.test.med.filt) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "none")+
  labs(x="Medians of Sex-Differences in Z Errors", y="Density Across 100 Replications")

z.sex_bias_density_plt2 <- z.sex.test.med %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat, scales="free") +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos, y=y_pos),
              data = t.test.z.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom") +
  labs(x="Medians of Sex-Differences in Z Errors", y="Density Across 100 Replications")
ggsave(filename="figs/z.sex_bias_density_plt2.png", z.sex_bias_density_plt2, height=6, width=14, units="in")
```

@@

#plots!
all_z_sum.df %>%
  dplyr::filter(dataset != "raw") %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="zer") +
  facet_grid(pheno_cat~source, scales="free_y") +
  geom_hline(data=all_z.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = max_val + 0.01),
              data = z.all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"),  name = "ComBat Configuration", labels=dataset_names) + 
  theme_linedraw()

@@

z_sex_boxplts <- all_z_sum.df_scaled %>%
  dplyr::filter(dataset != "raw") %>%
  mutate(source = factor(source, levels=c("low", "high"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_diff)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="zer") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=z_ext_list)) +
  geom_hline(yintercept=0, linetype="dashed")+
  geom_text(aes(label = sig_fdr, y = .07),
              data = z.all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Proportion Female", x = "Dataset")
ggsave("figs/z_sex_boxplts.jpeg", z_sex_boxplts)
```

@@

```{r}
noext.sex.test.z.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext.sex.test.z.df <- bind_rows(noext.sex.test.z.list)
```

simple bar-plot to count regions w sigificant sex-biases

```{r}
noext.sex.test.z.df %>%
  mutate(sig_fdr = factor(sig_fdr, ordered=TRUE, levels=c("TRUE", "FALSE"))) %>%
  ggplot(aes(x=perm, fill=sig_fdr)) +
  geom_bar() +
  #geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = c("lightblue", "red"))
```

@@

next.t.test.z.sex.test.med <- noext.sex.test.z.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(z.sex.test.med$dataset))*length(unique(z.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 150,
                           dataset=="cf.lm" ~ 320,
                           dataset=="cf.gam" ~ 330,
                           dataset=="cf.gamlss" ~ 125))

t.test.z.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig_fdr, fill=dataset), position="dodge")

next.t.test.z.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig_fdr, fill=dataset), position="dodge")

z.sex_bias_density_plt_noext <- noext.sex.test.z.med %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig_fdr, x= x_pos, y=y_pos),
              data = next.t.test.z.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Z-Score Errors", y="Density Across 100 Replications")
ggsave(filename="figs/z_sex_bias_density_plt_noext.png", z.sex_bias_density_plt_noext, height=7, width=10, units="in")
```

>>>>

```{r}
noext.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext.sex.test.df <- bind_rows(noext.sex.test.list) %>%
  mutate(sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

@@

```{r}
noext.sex.test.df %>%
  ggplot(aes(x=perm, fill=significant)) +
  geom_bar() +
  #geom_text(stat='count', aes(label=..count..)) +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_blank()) +
    scale_fill_manual(values = c("#EA6F5F", "#F3AEA6", "#5FDAEA"))
```

@@

next.t.test.cent.sex.test.med <- noext.sex.testmed %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(cent.sex.test.med$dataset))*length(unique(cent.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         sig = case_when(t.test.p < 0.001 ~ "***",
                               t.test.p >= 0.001 & t.test.p < 0.01 ~ "**",
                               t.test.p >= 0.01 & t.test.p < 0.05 ~ "*",
                               t.test.p >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 6,
                           dataset=="cf.lm" ~ 9,
                           dataset=="cf.gam" ~ 9.5,
                           dataset=="cf.gamlss" ~ 5))

t.test.cent.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig, fill=dataset), position="dodge")

next.t.test.cent.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig, fill=dataset), position="dodge")

sex_bias_density_plt_noext <- noext.sex.testmed %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff*100, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig, x= x_pos*100, y=y_pos),
              data = next.t.test.cent.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Centile Errors", y="Density Across 100 Replications")
ggsave(filename="figs/sex_bias_density_plt_noext.png", sex_bias_density_plt_noext, height=7, width=10, units="in")
```

@@

```{r}
z.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.sex.test.df <- bind_rows(z.sex.test.list) %>%
  mutate(sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

@@

```{r}
z.sex.test.df %>%
  ggplot(aes(x=perm, fill=significant)) +
  geom_bar() +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = c("#EA6F5F", "#F3AEA6", "#5FDAEA"))
```

@@

```{r}
#look by feature type
z.sex_bias_hist_plt <- z.sex.test.df %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss" | dataset == "cf.lm") %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  mutate(pheno = gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    perm = as.factor(sub("perm-0", "", perm))) %>%
ggplot() +
  geom_histogram(aes(x=median_sex_diff, color=perm, fill=perm), alpha=0.3, position="identity", bins=40) +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(pheno_cat~dataset, scales="free", labeller = labeller(dataset = as_labeller(dataset_names))) +
  theme_linedraw(base_size=12) +
  theme(legend.position = "none") +
  labs(x="Male - Female Median Centile Errors", y="Number of Features") +
  ggtitle("Sex differences in median z-score errors across 100 sampling replications")
ggsave(filename="figs/z.sex_bias_hist_plt.z.png", z.sex_bias_hist_plt)
```

@@

t.test.z.sex.test.med <- z.sex.test.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            t.test.stat = tidy(t.test(median_of_median_sex_diff))$statistic,
            t.test.df = tidy(t.test(median_of_median_sex_diff))$parameter,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(z.sex.test.med$dataset))*length(unique(z.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         sig = case_when(t.test.p < 0.001 ~ "***",
                               t.test.p >= 0.001 & t.test.p < 0.01 ~ "**",
                               t.test.p >= 0.01 & t.test.p < 0.05 ~ "*",
                               t.test.p >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 155,
                           dataset=="cf.lm" ~ 360,
                           dataset=="cf.gam" ~ 345,
                           dataset=="cf.gamlss" ~ 125))

#pretty table
t.test.z.sex.test.med_tbl <- t.test.z.sex.test.med %>%
  dplyr::select(dataset, pheno_cat, t.test.est, t.test.stat, t.test.df, t.test.p, sig, sig_fdr) %>%
  mutate(dataset = case_when(dataset == "cf" ~ "ComBat w/o Covariates",
                                   dataset == "cf.lm" ~ "Linear ComBat",
                                   dataset == "cf.gam" ~ "ComBat-GAM",
                                   dataset == "cf.gamlss" ~ "ComBatLS")) %>%
  rename("ComBat Method" = dataset,
         "Phenotype Category" = pheno_cat,
         "Estimate" = t.test.est,
         "t-statistic" = t.test.stat,
         "dfs" = t.test.df,
         "p-value" = t.test.p,
         "Significance" = sig,
         "Significance (FDR-corrected)" = sig_fdr) %>%
  gt() %>%
  tab_style(style = list(cell_fill(color = "gray95")),
    locations = cells_row_groups()) %>%
  tab_options(column_labels.font.weight = "bold") %>%
  tab_header(title = "One-sided t-tests of sex differences in z-score errors across 100 replications")
gtsave(t.test.z.sex.test.med_tbl, filename="figs/z_median_sexdiff_table.png")
```

@@

t.test.z.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig, fill=dataset), position="dodge")

z.sex_bias_density_plt <- z.sex.test.med %>%
  dplyr::filter(dataset != "cf") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig, x= x_pos, y=y_pos),
              data = t.test.z.sex.test.med.filt) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "none")+
  labs(x="Medians of Sex-Differences in Z Errors", y="Density Across 100 Replications")

z.sex_bias_density_plt2 <- z.sex.test.med %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat, scales="free") +
  theme_linedraw() +
  geom_text(aes(label = sig, x= x_pos, y=y_pos),
              data = t.test.z.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom") +
  labs(x="Medians of Sex-Differences in Z Errors", y="Density Across 100 Replications")
ggsave(filename="figs/z.sex_bias_density_plt2.png", z.sex_bias_density_plt2, height=6, width=14, units="in")
```

@@

#plots!
all_z_sum.df %>%
  dplyr::filter(dataset != "raw") %>%
  ggplot(aes(x=dataset, y=female_ratio)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="zer") +
  facet_grid(pheno_cat~source, scales="free_y") +
  geom_hline(data=all_z.sum_raw, aes(yintercept=female_ratio), linetype="dashed")+
  geom_text(aes(label = sig, y = max_val + 0.01),
              data = z.all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"),  name = "ComBat Configuration", labels=dataset_names) + 
  theme_linedraw()

@@

z_sex_boxplts <- all_z_sum.df_scaled %>%
  dplyr::filter(dataset != "raw") %>%
  mutate(source = factor(source, levels=c("low", "high"), ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=female_ratio_diff)) +
  geom_boxplot(aes(color=dataset)) +
  # geom_dotplot(binaxis = "y", stackdir="zer") +
  facet_grid(pheno_cat~source, scales="free_y", labeller = labeller(source=z_ext_list)) +
  geom_hline(yintercept=0, linetype="dashed")+
  geom_text(aes(label = sig, y = .07),
              data = z.all_t_test.df) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) + 
  theme_linedraw() +
  scale_x_discrete(labels=dataset_names) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Proportion Female", x = "Dataset")
ggsave("figs/z_sex_boxplts.jpeg", z_sex_boxplts)
```

@@

```{r}
noext.sex.test.z.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext.sex.test.z.df <- bind_rows(noext.sex.test.z.list) %>%
  mutate(sig_uncor = ifelse(p.value<0.05, TRUE, FALSE)) %>%
  mutate(significant = case_when(sig_fdr == TRUE ~ "Survives FDR Correction",
                                 sig_uncor == TRUE & sig_fdr == FALSE ~ "Uncorrected Only",
                                 sig_uncor == FALSE & sig_fdr == FALSE ~ "Not Significant")) %>%
  mutate(significant = factor(significant, ordered=TRUE, levels=c("Survives FDR Correction", "Uncorrected Only", "Not Significant")))
```

```{r}
noext.sex.test.z.df %>%
  ggplot(aes(x=perm, fill=significant)) +
  geom_bar() +
  facet_wrap(~dataset) +
  theme(axis.text.x = element_blank()) +
  scale_fill_manual(values = c("#EA6F5F", "#F3AEA6", "#5FDAEA"))
```

@@

next.t.test.z.sex.test.med <- noext.sex.test.z.med %>%
  group_by(dataset, pheno_cat) %>%
  summarise(t.test.p = tidy(t.test(median_of_median_sex_diff))$p.value,
            t.test.est = tidy(t.test(median_of_median_sex_diff))$estimate,
            x_pos = median(median_of_median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = length(unique(z.sex.test.med$dataset))*length(unique(z.sex.test.med$pheno_cat))),
                  sig_fdr = case_when(p.val_fdr < 0.001 ~ "***",
                               p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
                               p.val_fdr >= 0.01 & p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         sig = case_when(t.test.p < 0.001 ~ "***",
                               t.test.p >= 0.001 & t.test.p < 0.01 ~ "**",
                               t.test.p >= 0.01 & t.test.p < 0.05 ~ "*",
                               t.test.p >= 0.05 ~ ""),
         y_pos = case_when(dataset=="cf" ~ 150,
                           dataset=="cf.lm" ~ 320,
                           dataset=="cf.gam" ~ 330,
                           dataset=="cf.gamlss" ~ 125))

t.test.z.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig, fill=dataset), position="dodge")

next.t.test.z.sex.test.med %>%
  ggplot() +
  geom_col(aes(x=pheno_cat, y=sig, fill=dataset), position="dodge")

z.sex_bias_density_plt_noext <- noext.sex.test.z.med %>%
  #dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot() +
  geom_density(aes(x=median_of_median_sex_diff, fill=dataset, color=dataset), alpha=0.6, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed", color="#3F3F3F") +
  facet_wrap(~pheno_cat) +
  theme_linedraw() +
  geom_text(aes(label = sig, x= x_pos, y=y_pos),
              data = next.t.test.z.sex.test.med) +
  scale_fill_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  theme(legend.position = "bottom")+
  labs(x="Medians of Sex-Differences in Z-Score Errors", y="Density Across 100 Replications")
ggsave(filename="figs/z_sex_bias_density_plt_noext.png", z.sex_bias_density_plt_noext, height=7, width=10, units="in")
```
